Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
shortening arguments in section 5

\documentclass[11pt]{article}
%\documentclass{llncs}
\def\shownotes{1}

@@

\noindent
We can then argue that all $V_i$ simultaneously have individual entropy with good probability:
\begin{corollary}
\label{cor:samp sec}
 Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.  Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
\begin{proof}
Union bound over the probability in \lemref{lem:sampling works}.
%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
\end{proof}

@@

Thus, unless the choice of $\lambda$ is very unlucky,
\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. This allows us to conclude the following.
\begin{corollary}
\label{cor:samp unguess}
Let all the variables be as in \thref{thm:sampling}.
For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq H_0(C)$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
\end{proof}

\subsection{Correctness of \consref{cons:sampling}}
\label{sec:correct sampling}
The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.  This probability is at most $\ell/\mathcal{Z}^\eta$.   Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$. We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.  The proof is in \apref{sec:sampling errors}.

@@

\begin{corollary}
Let all the variables be as in \thref{thm:sampling}.
When
\[
\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
\]
and $(c, p)\leftarrow \gen(w)$, then
\[
\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
\]
That is, \consref{cons:sampling} is correct with overwhelming probability.
\end{corollary}

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
\Huse &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
\end{align*}
That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).  We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
%However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
\bibliographystyle{alpha}
\bibliography{crypto}

@@

It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.  Denote by $guess_{1}, ..., guess_q$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).  Note that $\sum_{i=1}^q \Pr[W_j = guess_i]\geq q/|\mathcal{Z}|$.  Suppose not, this means that there is some $guess_i$ with probability $\Pr[W_j = guess_i] < 1/|\mathcal{Z}|$.  Since there are $\mathcal{Z} - q $ remaining possible values of $W_j$ for their total probability to be at least $1-q/|\mathcal{Z}|$ at least of these values has probability at least $1/\mathcal{Z}$.  This contradicts the statement $guess_1,..., guess_q$ are the most likely values.  Consider $S$ that queries its oracle on $(j, guess_1),.., (j, guess_q)$.  Denote by $Guess$ the random variable when $W_j\in \{guess_1,.., guess_q\}$  After these queries the remaining min-entropy is at most:

>>>>

\documentclass[11pt]{article}
%\documentclass{llncs}
\def\shownotes{0}

@@

\noindent
We can then argue that all $V_i$ simultaneously have individual entropy with good probability~(by union bound):
\begin{corollary}
\label{cor:samp sec}
 Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}, and all the other variables be as in \thref{thm:sampling}.  Then $\Pr_{\lambda\leftarrow \Lambda}[\forall i, \Hoo(V_i | \Lambda = \lambda)  \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
%\begin{proof}
%Union bound over the probability in \lemref{lem:sampling works}.
%%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
%\end{proof}

@@

Thus, unless the choice of $\lambda$ is very unlucky,
\consref{cons:sampling} is \consref{cons:first construction} applied to an unguessable block distribution $V_1,..., V_\ell$. That is, 
\begin{corollary}
\label{cor:samp unguess}
Let all the variables be as in \thref{thm:sampling}.
For every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq H_0(C)$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{corollary}
%\begin{proof}
%Result of \corref{cor:v are unguessable} and \lemref{lem:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
%\end{proof}

\subsection{Correctness of \consref{cons:sampling}}
\label{sec:correct sampling}
The argument that $1\rightarrow 0$ flips from $c$ to $c'$ are unlikely carries over from \consref{cons:first construction}.  Recall that the code $C$ corrects up to $t'$ flips from $0$ to $1$. We now show that $C$ is up to the task with overwhelming probability, i.e., that  $\Pr_{(v, v')\leftarrow (V, V')}[v'\not\in\neigh_{t'}(v)] <\ngl(n)$.  The proof is in \apref{sec:sampling errors}.  The correctness argument in \thref{thm:sampling} is obtained by subtracting the probability of a single $1\rightarrow 0$ bit flip~($\ell/|\mathcal{Z}|$) and the error of the code~($\delta_{code}$).

@@

%\begin{corollary}
%Let all the variables be as in \thref{thm:sampling}.
%When
%\[
%\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\gamma/\eta)
%\]
%and $(c, p)\leftarrow \gen(w)$, then
%\[
%\Pr[\rep(w', p) = c] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
%\]
%That is, \consref{cons:sampling} is correct with overwhelming probability.
%\end{corollary}

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} can work for partial block sources when $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
\]
That is, \consref{cons:sampling} achieves $\Huse\le 0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$).  We note that for polynomial-size alphabets, \consref{cons:sampling} will still work as long as we use a code that corrects Hamming errors in both directions (with a polynomial size alphabet the probability of $1\rightarrow 0$ bits flips is noticeable); however, for a polynomial-size alphabet, $\Huse>0$.
%However, in this setting $\Huse =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
\bibliographystyle{alpha}
\bibliography{crypto}

@@

It suffices to show that there exists an $S$ making $q$ queries such that for some $j\in J, \Hav(W_j | S^{I_{W}(\cdot, \cdot)})\le \log |\mathcal{Z}| - \log q$.  Let $j\in J$ be some arbitrary element of $J$ and denote by $w_{j,1}, ..., w_{j,q}$ the $q$ most likely outcomes of $W_j$~(breaking ties arbitrarily).  Then $\sum_{i=1}^q \Pr[W_j = w_{j,i}]\geq q/|\mathcal{Z}|$.  Suppose not, this means that there is some $w_{j,i}$ with probability $\Pr[W_j = w_{j,i}] < 1/|\mathcal{Z}|$.  Since there are $\mathcal{Z} - q $ remaining possible values of $W_j$ for their total probability to be at least $1-q/|\mathcal{Z}|$ at least of these values has probability at least $1/\mathcal{Z}$.  This contradicts the statement $w_{j,1},..., w_{j,q}$ are the most likely values.  Consider $S$ that queries its oracle on $(j, w_{j,1}),.., (j, w_{j,q})$.  Denote by $Bad$ the random variable when $W_j\in \{w_{j,1},.., w_{j,q}\}$  After these queries the remaining min-entropy is at most:
